\chapter{Vorwort}

Hoi, Chummers!

Willkommen in meinem kleinen Wust aus Aufzeichnungen, Vorbereitungen und dergleichen für die Shadowrun Kampagne meiner Runner und mir, ihrem Spielleiter. Meine Matrix-Persona ist \textit{MarauderPixie} und mein echter Name tut hier nichts zur Sache. Falls ihr unbedingt einen braucht, koennt ihr mich auch Mr. Johnson nennen.

Bis auf weiteres ist dies nur eine copy-pasted Version \textit{simple edition (SE)} von \textbf{SIXTH WORLD}, die sich zum Zeitpunkt des Kopierens (18. Jan. 2023) unter \url{https://swse.neocities.org/} findet. Soweit ich sagen kann, basiert die SE auf der \textit{Digest Edition 1.2} mit einigen Reduktionen. Die SIXTH WORLD Vibes lehnen stark in Richtung Shadowrun 1-3, ich werde das Ganze stärker Richtung sechster Edition ausrichten. Mein Ziel ist es also, die Regeln im Laufe der Zeit anzupassen, zu kürzen oder zu erweitern und letzlich auch zu uebersetzen. Den Anfang machen dabei ein paar Bezeichnungsänderungen (XP zu Karma zB) und die Reduktionen der SE sozusagen rueckgaengig zu machen, d.h. z.B. Moves aus der Digest Edition 1.3 oder anderen Derivaten hinzuzufügen. Abgesehen davon, werden wir sehen, wohin es gehen wird. 

\section{Changelog}

\begin{easylist}
# added archetype descriptions from v26 to the dossiers
# renamed 'Natural Spirits' to 'Nature Spirits'
# minor changes (mostly condensing) to Dossiers
# rephrased the Ammo section in chapter 'Combat'
# (re-)added a few metatype moves
# use an array of stats instead of loosely assignable points
# changed 'mark XP' to 'receive Karma' (in chapters 1-3)
# changed 'Karma' to 'Edge' (in chapters 1-3), as is customary when doing this
# changed 'Hacker' to 'Decker'; that's just how we roll (talking about respecting the canon...)
# removed the option to \textit{awaken} from the \skill{Advance} Move, since awakening just like that isn't really canonical
# minor semantics
\end{easylist}


\section{Vorwort des Originals}

Sixth World is a ``hack'' of the game Dungeon World which attempts to capture the flavor of the world of the well-known RPG Shadowrun®.

The Sixth World is the dangerous and grim future of our own world, where magic has resurfaced, megacorporations rule the world, and humanity has perfected incredible new technological capabilities including advanced cybernetics and the worldwide virtual reality network called the Matrix.

This game assumes familiarity with Shadowrun, as well as with Dungeon World.

\subsection{Disclaimer}

Dungeon World is the property of Sage LaTorra and Adam Koebel, and is available under the Creative Commons Attribution 3.0 Unported License. See www.dungeon-world.com for details.

The Topps Company, Inc. has sole ownership of the names, logo, artwork, marks, photographs, sounds, audio, video and/or any proprietary material used in connection with the game Shadowrun. This is a fan-created adaptation, and no challenge is intended toward Topp’s ownership of the Shadowrun intellectual property.

\subsection{Simple Edition Notes}

This is simplified edition of Sixth World by Chris Clouser and Tanner Yea. The original used to be possible to find on http://waryjack.com/sw/ but now it seems to have disappeared. PDF is still available on dropbox.

This edition is very similar however – I see myself more as an editor and final beta-tester than new autor, and I aim to make the game (already excellent before I got to it) “production quality”.

– Wrb, wrb@autistici.org